From noise to knowledge: how randomness generates novel phenomena and information

### 2017-10-24 paper.Rmd
passable rendering of fonts on linux, though looks like a different font is getting swapped in.

```{r include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)
library(ggthemes)
library(tidyverse)
library(cowplot)
#library(hrbrthemes)
#extrafont::loadfonts()
#ggplot2::theme_set(hrbrthemes::theme_ipsum_rc())
#hrbrthemes::import_roboto_condensed()

ggplot2::theme_set(theme_cowplot())
```

@@

library(cowplot)
ggdraw() +
  draw_plot(p2, x = 0, y = 0, width = 1, height = 0.5) +
  draw_plot(p1, x = 0, y = .5, width = 1, height = 0.5)
ggsave("figures/tipping.pdf")
```

>>>>

```{r include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE)
library(ggthemes)
library(tidyverse)
library(cowplot)
library(hrbrthemes)
hrbrthemes::import_roboto_condensed()
extrafont::loadfonts()
ggplot2::theme_set(hrbrthemes::theme_ipsum_rc())
#ggplot2::theme_set(theme_cowplot())
```

@@

library(cowplot)
ggdraw() +
  draw_plot(p2, x = 0, y = 0, width = 1, height = 0.5) +
  draw_plot(p1, x = 0, y = .5, width = 1, height = 0.5)
#ggsave("figures/tipping.pdf")
```
